### 2024-02-24 paper/methods.qmd
map bigram analysis over datasets
format methods doc for BJPS

@@

To take advantage of the scale of the ST corpus, we used machine learning to impute or estimate support or opposition across *[all]* 20,787 comments, using the `tidymodels` framework *[software versions]*.

@@

>>>>

---
format:
  pdf:
    mainfont: "Times New Roman"
    fontsize: "12pt"
    geometry: 
      - "margin = 1in"
    linestretch: 1.5
---

@@

To take advantage of the scale of the ST corpus, we used a machine learning model to impute or estimate support or opposition across *[all]* 20,787 comments, using the `tidymodels` framework *[software versions]*.

@@

## Text analysis

Text analysis was conducted as reported in the main text, with code written in R *[version]* and making extensive use of the `tidyverse` suite *[version]*.

## Data and code availability

The full data collection and analysis code is available at *[github]*.  To facilitate reproduction and reuse, *[separate data repo]*

- raw ST scrape results? 
- 03 raw text and annotation files
- 06 manual coding
- 08 fitted model and imputed dataset
